---
title: "Course Summary"
author: "Martin Morgan"
date: "October 21, 2016"
output: html_document
---

## Day 1: Packages and Version Control 

We learned to create a package using [devtools][1]. The way to
get started is to create the skeleton of a package.

```
library(devtools)
create("Elbo")
```

This creates a directory with a couple files and a folder.
We then did the following:

1. The DESCRIPTION contains info about the package; we edited
   it for our purposes.
2. We looked at the NAMESPACE, but didn't touch it
3. We created our first function in the R folder, `hi()`.

We then used [roxygen2][] to add documentation to the function,
including information about parameters and return values.
We also used tags (`@export`) to indicate that we wanted to 
'export' the function from the namespace.

We also learned to manage our source code using [github][].

Here's the result of our work:

```{r our-package}
library(Elbo)
hi("Martin")
```

## Day 2: Classic, Rich, and Tidy data

'Classic' data is represented as a `data.frame()` with
samples as rows and features as columns.

```{r}
pdatafl = "~/a/Elbo/ALL-phenoData.csv"
exprfl = "~/a/Elbo/ALL-expression.csv"
classic <- input_classic(pdatafl, exprfl)
classic[1:5, c(1:3, 22:24)]
```

One of the things we did was to plot the distribution of 
expression values across genes

```{r classic-exprs-hist}
hist(colMeans(classic[, -(1:22)]))
```

[1]: https://cran.r-project.org/package=devtools
[roxygen2]: https://cran.r-project.org/package=roxygen2
[github]: https://github.com